 \vspace{4cm}
 At this point, we have all the necessary tools to describe the results
 of this thesis.
 The first one, reported in Chapter 5, is a gravitational wave-like propa
gation on the top of an acoustic metric. Notably, in the past only static
 solutions of GR were designed in analogue models. Here,
 we present a system where analogue gravitational waves propagate sat
isfying Einstein’s equations.
 The second result, in Chapter 6, consists in designing a system in which
 an acoustic horizon is excited by a gravitational wave-like perturbation.
 To this purpose, we choose a cylindrical acoustic black hole, where we
 introduce an appropriate extension in the geometry of the previously
 found gravitational wave-like perturbation.


\newpage
\section{Results 1}

blablabla....



To summarize, in this chapter we have shown how to design a system where the
 analogue of a gravitational wave propagates on the top of an acoustic flat metric.
 Remarkably, this perturbation satisfies Einstein’s equations in vacuum, being it a
 perturbation with the same space-time dependence as the gravitational wave one
 propagating on the same flat background. This is the first time that the dynamics
 of a gravitational scenario is reproduced in an analogue model. The ability to
 reproduce a gravitational wave in an analogue system is a relevant achievement for
 its interesting implications. To start with, we can think of simulating a gravitational
 wave over a metric with an acoustic horizon: this is what we study in the next
 chapter. In Chapter 6 we indeed design a system where an analogue black hole is
 excited by an impinging gravitational wave-like perturbation. To do that we use the
 analogue gravitational wave found in this chapter through transformation I (c). We
 choose to work with this specific case because there everything is considered up to
 O(), while for the other transformations dominant terms are of order O().

\section{Results 2}



blablabla....


To summarize, in this chapter we have developed the description of an acoustic
 cylindrical black hole perturbed by a gravitational wave-like perturbation. This
 perturbation is introduced as the cylindrical extension of the analogue gravitational
 wave found in Chapter 5. After having illustrated the designed physical system,
 we have studied how the acoustic horizon is perturbed by the impinging analogue
 gravitational wave, computing also its generators. This analogue model is important
 since it allows to study how an acoustic horizon responds to a gravitational wave-like
 perturbation.